FraCaS: Temporal Analysis

### 2020-05-26 paper2020/paper.tex
minor

Our interpretation is cast withing the framework of a largely standard
montagovian semantics \cite{todo}. In brief, sentences are interpreted as
propositions, verbs and noun-phrases as predicates.  We use
type-raising of noun-phrases, to support quantifiers~\cite{PTQ}.

@@

The issue is that the quantification introduced by the temporal marker
is outside the negation. For example, the premiss of (038) is
interpreted as ``there exists a time in the past when every delegate
did not finish the report'' --- which is incorrect in this context.
\fracasex{038}{
\item	No delegate finished the report.
\hyp 	Some delegate finished the report on time.
}
%
We stress that such interaction between quantifiers and negation
already occurs without temporal analysis: one must make a difference
between narrow scoping and wide scoping \cite{todo}. Unfortunately,
the montagovian system over which we base our implementaiton does not
support this phenomena. (Indeed the test suite does not appear to
handle this case). We propose that the situation becomes
quantitatively more difficult to handle with the added complication of
time-quantification, but not fundamentally different.
%
A similar issue occurs with group readings, which are interpreted as
conjunctions. Here, the problem is to solve the order of scoping
between this conjunction and time-interval quantifiers.

>>>>

Our interpretation is cast within the framework of a largely standard
montagovian semantics \cite{todo}. In brief, sentences are interpreted as
propositions, verbs and noun-phrases as predicates.  We use
type-raising of noun-phrases, to support quantifiers~\cite{PTQ}.

@@

The issue is that the quantification introduced by the temporal marker
is outside the negation. For example, the premiss of (038) is
interpreted as ``there exists a time in the past when every delegate
did not finish the report'' --- which is incorrect in this context.
\fracasex{038}{
\item	No delegate finished the report.
\hyp 	Some delegate finished the report on time.
}
%
We stress that such interaction between quantifiers and negation
already occurs without temporal analysis: one must make a difference
between narrow scoping and wide scoping \cite{todo}. Unfortunately,
the montagovian system over which we base our implementaiton does not
support this phenomena. (Indeed the test suite does not appear to
handle this case). \todo{You mean the system? It seems unclear what you are talking and in what way a test suite is not handling an example. It does not exist or?} We propose that the situation becomes
quantitatively more difficult to handle with the added complication of
time-quantification, but not fundamentally different.
%
A similar issue occurs with group readings, which are interpreted as
conjunctions. Here, the problem is to solve the order of scoping
between this conjunction and time-interval quantifiers.
